Inferring generation-interval distributions from contact tracing data

### 2018-09-24 doc/network.tex
update

First, we compared the four methods by simulating a stochastmic epidemic model homogeneous network with 100000 individuals using Ebola-like parameters for 15 weeks (Figure~?).

>>>>

First, we compared how the estimates from the two methods vary across time using a single stochastic simulation on a homogeneous network (Figure~\ref{fig:example}).
As expected, we find that using the observed generation-interval distributions always underestimates both the mean generation interval and the reproductive number;
due to initial overestimation of the growth rate,

\begin{figure}
\includegraphics[width=\textwidth]{../fig/example.pdf}
\caption{Fill this out.}
\label{fig:example}
\end{figure}
